Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-07-18 awipev-CO2.Rmd
ph plots updated

#plot for POSTER june 2019
#plot of pH seafet
poster_ph <- ggplot() +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
  labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
  theme(legend.position= c(0.17, 0.8),
                     legend.text=element_text(size=14),
                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
                      axis.text=element_text(size=15),
                      plot.margin = unit(c(1,1,1,1), "cm"),
                      axis.title.x= element_text(size =15),
                      legend.title=element_blank())

print(poster_ph)
ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")

@@

size_point <- 0.4 # size of data points
plot_range_dur <-
  ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(plot_range_dur)
ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
```
The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).

@@

### **Calculated vs Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal,temp, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

# DURAFET vs CALC
pdur_calc_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pH_calc_norm4, label = month))+
  geom_text( aes(color=factor(month))) + 
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH calculated vs pH durafet, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
   coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2)) + scale_color_discrete(guide="none")+
  labs(x="pH durafet, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
pdur_calc_norm_text

@@

### **Calculated / seaFET pHs**
```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
# SEAFET vs CALC
psf_calc_norm_text <-  ggplot(d_all,aes(x=pHint_tot_sf_norm4, y= pH_calc_norm4, label = month))+
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH calculated vs pH seaFET, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
  labs(x="pH seaFET, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
psf_calc_norm_text

seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_norm4)
seafet_calc_contros_xts <- as.xts(seafet_calc_contros_xts, order.by = d_all$datetime)
dygraph(seafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH seaFET, normalized at 4°C", ylab="pHT") %>%
    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
```

## SNAPO-CO2
Since November 2018, informations on weekly Ferrybox and monthly durafet/seaFET samplings are collected in a online document that can be consulted at anytime:

>>>>

# #plot for POSTER june 2019
# #plot of pH seafet
# poster_ph <- ggplot() +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
#   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
#   theme(legend.position= c(0.17, 0.8),
#                      legend.text=element_text(size=14),
#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
#                       axis.text=element_text(size=15),
#                       plot.margin = unit(c(1,1,1,1), "cm"),
#                       axis.title.x= element_text(size =15),
#                       legend.title=element_blank())
# 
# print(poster_ph)
# ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")

@@

size_point <- 0.4 # size of data points
plot_range_dur <-
  ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(plot_range_dur)
ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
```

The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).

@@

### **Calculated / Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal,temp, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

# DURAFET vs CALC
fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pH_durafet_norm4 , nperm = 99)

pdur_calc_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pH_calc_norm4, label = month))+
  geom_text( aes(color=factor(month))) + 
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH calculated vs pH durafet, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
   coord_fixed(ratio = 1 , xlim=c(8,8.22), ylim=c(8,8.22)) + 
  scale_color_discrete(guide="none")+
  labs(x="pH durafet, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
pdur_calc_norm_text

@@

### **Calculated / seaFET pHs**
```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
# SEAFET vs CALC
fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pHint_tot_sf_norm4 , nperm = 99)

psf_calc_norm_text <-  ggplot(d_all,aes(x=pHint_tot_sf_norm4, y= pH_calc_norm4, label = month))+
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH calculated vs pH seaFET, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
  labs(x="pH seaFET, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
psf_calc_norm_text

seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_norm4)
seafet_calc_contros_xts <- as.xts(seafet_calc_contros_xts, order.by = d_all$datetime)
dygraph(seafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH seaFET, normalized at 4°C", ylab="pHT") %>%
    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
```
### **Spectro / durafet**

```{r pHs comparaison durafet spectro, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / durafet
fit <- lmodel2(data = d_all,  pH_s_durafet_temp_field ~ pH_durafet_corrected , nperm = 99)

p_dura_spectro <-  ggplot(d_all,aes(x=pH_durafet_corrected, y= pH_s_durafet_temp_field, label = month))+
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
  labs(x="pH durafet", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
p_dura_spectro
```

### **Spectro / seaFET**

```{r pHs comparaison sf spectro, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / seafet
fit <- lmodel2(data = d_all,  pH_s_seafet_temp_field ~ pHint_tot_sf , nperm = 99)

p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_field, label = month))+
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH spectro vs pH seaFET","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
  labs(x="pH seaFET", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
p_sf_spectro
```
## SNAPO-CO2
Since November 2018, informations on weekly Ferrybox and monthly durafet/seaFET samplings are collected in a online document that can be consulted at anytime:
